Determinism, Complexity, and Predictability in Computer Performance

### 2014-03-14 related.tex
mark related stuff as editable

\section{Related Work }\label{sec:related}
{\color{red}[[NOT EDITABLE]]}
Attempting to model time series for prediction is an old problem which arguably began with Yule in 1927 when he invented autoregression \cite{Yule27}. Since then hundreds if not thousands of prediction strategies have been developed for a wide variety of prediction tasks. The purpose of this paper is \emph{not} to model a time series for prediction but to understand the predictability of a real-valued-scalar time series model free and then to associate the prediction accuracy with the time series inherent complexity.

@@

>>>>

\section{Related Work }\label{sec:related}
{\color{blue}[[EDITABLE]]}
Attempting to model time series for prediction is an old problem which arguably began with Yule in 1927 when he invented autoregression \cite{Yule27}. Since then hundreds if not thousands of prediction strategies have been developed for a wide variety of prediction tasks. The purpose of this paper is \emph{not} to model a time series for prediction but to understand the predictability of a real-valued-scalar time series model free and then to associate the prediction accuracy with the time series inherent complexity.

@@

The permutation entropy has been used in the past to detect
